---
title: "Shiny Application and Reproducible Pitch"
author: "Chen Xu"
date: "MAY 3, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the Course Project

This is a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

Instructions:

Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
Deploy the application on Rstudio's shiny server
Share the application link by pasting it into the provided text box
Share your server.R and ui.R code on github

## How to use the application

Using the data of stock information containing 5 industry giants, we plot the tendency of the stocks and correlation between each stock.

The application is running on (https://chenxumark.shinyapps.io/Stock/)

ui.R, and Server.R Code in my github repository (https://github.com/chenxumark/Developing-Data-Products)

## Stock Dataset from Rawgit

The data used in the app comes from the Rawgit websit.

```{r echo = TRUE}
stockdata <- read.csv("https://cdn.rawgit.com/plotly/datasets/master/stockdata.csv")
summary(stockdata)
```

## Plot
```{r echo=FALSE,message = FALSE}
    library(plotly)
  # Create dates
  stockdata$Date <- as.Date(stockdata$Date)
  
  # Reshape
  ds <- reshape2::melt(stockdata, id = "Date")
  ds <- filter(ds, variable != "GSPC")
  
  # Set some colors
  plotcolor <- "#F5F1DA"
  papercolor <- "#E3DFC8"
  
p <- plot_ly(source = "source") %>% 
      add_lines(data = ds, x = ~Date, y = ~value, color = ~variable, mode = "lines", line = list(width = 3))
    
    # Add SP500
    p <- p %>%
      add_lines(data = stockdata, x = ~Date, y = ~GSPC, mode = "lines", yaxis = "y2", name = "SP500", opacity = 0.3,
                line = list(width = 5)) %>% 
      layout(title = "Stock prices for different stocks overlaid with SP500",
             xaxis = list(title = "Dates", gridcolor = "#bfbfbf", domain = c(0, 0.98)),
             yaxis = list(title = "Stock Price", gridcolor = "#bfbfbf"), 
             plot_bgcolor = plotcolor,
             paper_bgcolor = papercolor, 
             yaxis2 = list(title = "SP500", side = "right", overlaying = "y"))
```

```{r pressure}
    p
```

